---
title: "Getting Started with myrpackage"
author: "Diogo Ribeiro"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started with myrpackage}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(myrpackage)
```

## Introduction

The `myrpackage` package provides simple greeting functions that demonstrate proper R package structure and documentation. This vignette introduces the main functionality of the package and shows examples of how to use it.

## Basic Usage

The package contains two main functions:

- `hello()`: Say hello in various languages
- `goodbye()`: Say goodbye in various languages

### Saying Hello

The `hello()` function generates a friendly greeting. By default, it says "Hello, world!":

```{r}
hello()
```

You can customize the greeting with a different name:

```{r}
hello("R Users")
```

### Multilingual Greetings

Both functions support multiple languages. Currently supported languages are:

- English (default)
- Spanish
- French
- Portuguese

Here are examples of greetings in different languages:

```{r}
hello("amigos", language = "spanish")
hello("mes amis", language = "french")
hello("amigos", language = "portuguese")
```

### Customizing Punctuation

You can also control whether the greeting ends with an exclamation mark:

```{r}
hello(exclamation = TRUE)  # Default
hello(exclamation = FALSE)
```

### Saying Goodbye

The `goodbye()` function works similarly to `hello()`, but provides farewell messages:

```{r}
goodbye()
goodbye("R Users")
goodbye("amigos", language = "spanish")
goodbye("mes amis", language = "french", exclamation = FALSE)
```

## Advanced Usage

Both functions perform input validation to ensure proper usage:

```{r, error=TRUE}
# These will generate errors:
hello(name = c("world", "everyone"))
hello(language = 123)
hello(exclamation = "yes")
```

## Further Reading

For complete details about function arguments and behavior, refer to the function documentation:

```{r, eval=FALSE}
?hello
?goodbye
```

## Conclusion

`myrpackage` is a simple demonstration package that showcases proper R package development practices. It includes:

- Well-documented functions
- Comprehensive tests
- Properly structured package components
- Vignettes for user documentation

While the functionality is minimal, the package structure follows best practices for R package development.
